Leadership across cultures and contexts: an exploratory analysis

### 2020-05-03 leadership_across_cultures_contexts.Rmd
Capitalized and italicized some variable names.

For each of the `r length(c(quality_vars, function_vars, leader_cost_vars, leader_benefit_vars, follower_benefit_vars, follower_cost_vars))` coded variables (see Tables \@ref(tab:qualfuncvars) and \@ref(tab:costbenefitvars)), we computed the proportion of text records (95% CI) that provided support using logistic mixed effects models that controlled for one possible source of bias -- publication date -- as a fixed effect, and included authors nested within cultures as random intercepts. We then computed the proportion of cultures with at least one text record providing support for that variable (calculating 95% CI using a cluster bootstrap). See Figure \@ref(fig:varsupport). For a table of all coefficients and 95% CIs, see Supplementary Table \@ref(tab:glmmcoefs).

@@

To investigate variation in functions, qualities, costs, and benefits, we fit a multiple logistic mixed effects regression model of each variable as a function of subsistence strategy, continental region, leader sex, and group structure, with random intercepts for author nested within culture. We then compared the AIC value of each model to a model with only the fixed and random intercepts, retaining `r nrow(multi_aic)` models that showed at least a two-point reduction in AIC value. We then created heatmaps that displayed the relative estimated marginal means for each level of these categorical explanatory variables for each outcome variable. See Figures \@ref(fig:heatmapsubsis), \@ref(fig:heatmapregion), \@ref(fig:heatmapsex), and \@ref(fig:heatmapgroups), and Tables \@ref(tab:variablevars) and \@ref(tab:universalvars).

For subsistence strategy, hunter-gatherers had relatively more evidence for polygyny, mating benefits, no coercive authority, political appointments and military command than other subsistence strategies. Pastoralists had more evidence for ritual functions, supernatural, aggressiveness and high quality spouse. Hunter-gatherers and pastoralists both had more evidence for high status, providing counsel/direction, and providing subsistence. The remaining subsistence strategies generally had relatively less evidence for all variables, except that the mixed strategy had relatively more evidence for organizing cooperation, distributing resources, and prosocial investment. See Figure \@ref(fig:heatmapsubsis).

For continental region, there was little strong patterning, except that Africa generally had relatively less evidence for any retained variable except providing counsel/direction, and South America had relatively more evidence for several variables, including age, social services, and high status. See Figure \@ref(fig:heatmapregion).

There was strong patterning of relative evidence for almost all variables by leader sex. Female leaders had relatively more evidence for high quality spouse, mating benefit, polygyny, high status, and age. Male leaders had relatively more evidence for social services, political appointments, prosocial investment, and loss of social services. Records pertaining to both sexes had relatively more evidence for organizing cooperation, providing subsistence, ritual functions, bravery, experience/accompished, and few that overlapped with males, such as military command and distributing resources. See Figure \@ref(fig:heatmapsex).

There was also strong patterning of relatively evidence for almost all variables by group structure. There was relatively more evidence for military traits in military groups, relatively more evidence for ritual and supernatural traits in relgious groups, relatively more evidenc for organizing cooperation and providing subsistence in economic groups, and so forth. Kin groups had relatively more evidence for providing counsel/direction, prosocial investment, age, and high status. Community and residential groups had relatively low evidence for most variables, except that there was relatively more evidence for high quality spouses among residential group leaders. See Figure \@ref(fig:heatmapgroups).

>>>>

For each of the `r length(c(quality_vars, function_vars, leader_cost_vars, leader_benefit_vars, follower_benefit_vars, follower_cost_vars))` coded variables (see Tables \@ref(tab:qualfuncvars) and \@ref(tab:costbenefitvars)), we computed the proportion of text records (95% CI) that provided support using logistic mixed effects models that controlled for one possible source of bias -- publication date -- as a fixed effect, and included authors nested within cultures as random intercepts. We then computed the proportion of cultures with at least one text record providing support for that variable (calculating 95% CI using a cluster bootstrap). See Figure \@ref(fig:varsupport). For a table of all coefficients and 95% CIs, see Table S\@ref(tab:glmmcoefs).

@@

To investigate variation in functions, qualities, costs, and benefits, we fit a multiple logistic mixed effects regression model of each variable as a function of subsistence strategy, continental region, leader sex, and group structure, with random intercepts for author nested within culture. We then compared the AIC value of each model to a model with only the fixed and random intercepts, retaining `r nrow(multi_aic)` models that showed at least a two-point reduction in AIC value. We then created heatmaps that displayed the relative estimated marginal means for each level of these categorical explanatory variables for each outcome variable. See Figures S\@ref(fig:heatmapsubsis), S\@ref(fig:heatmapregion), S\@ref(fig:heatmapsex), and S\@ref(fig:heatmapgroups), and Tables S\@ref(tab:variablevars) and S\@ref(tab:universalvars).

For subsistence strategy, hunter-gatherers had relatively more evidence for *Polygyny*, *Ledaer-Mating benefits*, *No coercive authority*, *Political appointments* and *Military command* than other subsistence strategies. Pastoralists had more evidence for *Ritual functions*, *Supernatural*, *Aggressiveness* and *High quality spouse*. Hunter-gatherers and pastoralists both had more evidence for *High status*, *Providing counsel/direction*, and *Providing subsistence*. The remaining subsistence strategies generally had relatively less evidence for all variables, except that the mixed strategy had relatively more evidence for *Organize cooperation*, *Distribute resources*, and *Prosocial investment*. See Figure S\@ref(fig:heatmapsubsis).

For continental region, there was little strong patterning, except that Africa generally had relatively less evidence for any retained variable except *Provide counsel/direction*, and South America had relatively more evidence for several variables, including *Age*, *Follower-Social services benefits*, and *High status*. See Figure S\@ref(fig:heatmapregion).

There was strong patterning of relative evidence for almost all variables by leader sex. Female leaders had relatively more evidence for *High quality spouse*, *Leader - Mating benefits*, *Polygyny*, *High status*, and *Age*. Male leaders had relatively more evidence for *Follower - Social  services benefits*, *Political appointments*, *Prosocial investment*, and *Leader-Social services costs*. Records pertaining to both sexes had relatively more evidence for *Organize cooperation*, *Providing subsistence*, *Ritual functions*, *Bravery*, *Experience/accompished*, and few that overlapped with males, such as *Military command* and *Distributing resources*. See Figure S\@ref(fig:heatmapsex).

There was also strong patterning of relative evidence for almost all variables by group structure. There was relatively more evidence for military traits in military groups, relatively more evidence for ritual and supernatural traits in relgious groups, relatively more evidence for organizing cooperation and providing subsistence in economic groups, and so forth. Kin groups had relatively more evidence for *Provide counsel/direction*, *Prosocial investment*, *Age*, and *High status*. Community and residential groups had relatively low evidence for most variables, except that there was relatively more evidence for *High quality spouses* among residential group leaders. See Figure S\@ref(fig:heatmapgroups).
